---
title: 'So Many Species, So Little Time: Measuring Biodiversity'
author: "Margaret Slein, Jory Griffiths, Egor Katkov"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = F, warning=F, message=F, echo=F)
```



Ecologists are often interested in the effects of perturbations (e.g. fires, logging, flooding or pollution) on biodiversity. 
However, boiling biodiversity down to a single metric can be difficult.
With the help of the Turkey lake dataset of benthic invertebrates [@Reference], we will present you with a number of common metrics, their meaning, and how they can be visualized with the help of a Rank-Abundance curves. 
You will then have the option to learn to do it yourself using an R package called codyn.

# The Data



# Species Richness

Perhaps the simplest measure of biodiversity is species richness. 
Simply count the number of species with an abundance greater than $0$.

```{r exercise=T}
# Exercise on calculating species richness?
```